---
title: "Figure 4 Code"
output: html_document
date: "2023-05-13"
---


```{r global-options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

```{r loading libraries, include=FALSE}
# This code chunk loads various libraries necessary to complete the data analysis and produce graphics
library(tidyverse)
library(stringr)
library(ez)
library(cowplot)
library(viridis)
library(viridisLite)
library("readxl")
library("ggcorrplot")
library(dplyr)
library(ltm)
library(plotrix)
library("viridis")
library("paletteer")
library(ggpubr)
library(rstatix)
library(lme4)
#install.packages("lmerTest")
library(lmerTest)
```

```{r reading data, include=FALSE}
#This data chunk loads and tidies up the data

#This loads the data file as the variable "data"
data <- read.csv('/Users/yasminebassil/Desktop/Data/averaged_results.csv')
# Tidying up the data
names(data)[1] <- 'index'
names(data)[2] <- 'Participant'
names(data)[3] <- 'Block_num'
names(data)[4] <- 'Total_Time'
names(data)[5] <- 'Orientation_Time'
names(data)[6] <- 'Navigation_Time'
names(data)[7] <- 'Distance'
names(data)[8] <- 'Speed'
names(data)[9] <- 'Mean_Dwell'
names(data)[10] <- 'Var_X'
names(data)[11] <- 'Var_Y'
names(data)[12] <- 'Var_Z'
names(data)[13] <- 'Teleportations'
data <- data[ -c(1) ]
data$Block_num <- as.factor(data$Block_num)
sapply(data, class)
data
```

```{r reading more data, include=FALSE}
#This loads the data file as the variable "data"
nav_data <- read.csv('/Users/yasminebassil/Desktop/Data/merged_results.csv')
# Tidying up the data
names(nav_data)[1] <- 'index'
names(nav_data)[2] <- 'Participant'
names(nav_data)[3] <- 'Block_num'
names(nav_data)[4] <- 'Target_Name'
names(nav_data)[5] <- 'Total_Time'
names(nav_data)[6] <- 'Orientation_Time'
names(nav_data)[7] <- 'Navigation_Time'
names(nav_data)[8] <- 'Distance'
names(nav_data)[9] <- 'Speed'
names(nav_data)[10] <- 'Mean_Dwell'
names(nav_data)[11] <- 'Var_X'
names(nav_data)[12] <- 'Var_Y'
names(nav_data)[13] <- 'Var_Z'
names(nav_data)[14] <- 'Teleportations'
nav_data <- nav_data[ -c(1) ]
nav_data$Block_num <- as.factor(nav_data$Block_num)
sapply(nav_data, class)

desired_order <- c("Automobile shop", "Police station ", "Fire Station", "Bank", "Pawn Shop", "Pizzeria", "Quattroki Restaurant", "High School")
# Reorder the levels of Target_Name
nav_data$Target_Name <- factor(nav_data$Target_Name, levels = desired_order)

#This loads the data file as the variable "data"
non_nav_data <- read.csv('/Users/yasminebassil/Desktop/Data/non_nav_data.csv')
# Tidying up the data
names(non_nav_data)[1] <- 'Participant'
names(non_nav_data)[2] <- 'Age'
names(non_nav_data)[3] <- 'PSQI'
names(non_nav_data)[4] <- 'SSS_Pre'
names(non_nav_data)[5] <- 'SSS_Post'
names(non_nav_data)[6] <- 'SBSOD'
names(non_nav_data)[7] <- 'MiniCog'
names(non_nav_data)[8] <- 'TrailsA'
names(non_nav_data)[9] <- 'TrailsB'
names(non_nav_data)[10] <- 'SetShifting'
names(non_nav_data)[11] <- 'CorsiBlocks'
names(non_nav_data)[12] <- 'SSQ_Pre'
names(non_nav_data)[13] <- 'SSQ_Post'
names(non_nav_data)[14] <- 'NARA'
non_nav_data <- head(non_nav_data, n=23)
```


```{r organizing data, include=FALSE}
b1 <- subset(nav_data, Block_num == 1)
rownames(b1) <- NULL 
b2 <- subset(nav_data, Block_num == 2)
rownames(b2) <- NULL 
b3 <- subset(nav_data, Block_num == 3)
rownames(b3) <- NULL 

change <- subset(b3, select = c(Participant, Target_Name))

for (i in 1:nrow(b3)) {
  change$Total_Time[i] <- b3$Total_Time[i] - b1$Total_Time[i]
  change$Orientation_Time[i] <- b3$Orientation_Time[i] - b1$Orientation_Time[i]
  change$Navigation_Time[i] <- b3$Navigation_Time[i] - b1$Navigation_Time[i]
  change$Distance[i] <- b3$Distance[i] - b1$Distance[i]
  change$Speed[i] <- b3$Speed[i] - b1$Speed[i]
  change$Mean_Dwell[i] <- b3$Mean_Dwell[i] - b1$Mean_Dwell[i]
  change$Var_X[i] <- b3$Var_X[i] - b1$Var_X[i]
  change$Var_Y[i] <- b3$Var_Y[i] - b1$Var_Y[i]
  change$Var_Z[i] <- b3$Var_Z[i] - b1$Var_Z[i]
  change$Teleportations[i] <- b3$Teleportations[i] - b1$Teleportations[i]
}

b1$Target_Name <- factor(b1$Target_Name, levels = desired_order)
b2$Target_Name <- factor(b2$Target_Name, levels = desired_order)
b3$Target_Name <- factor(b3$Target_Name, levels = desired_order)
change$Target_Name <- factor(change$Target_Name, levels = desired_order)
```


# Total Time

## Plot
```{r ct}
#Data.summary for Total_Time
data.summary <- data %>%
  group_by(Block_num) %>%
  summarise(
    se = std.error(Total_Time),
    Total_Time = mean(Total_Time)
  )
#Total_time by Block_num
p_ct <- ggplot(data, aes(x=Block_num, y=Total_Time, color=Participant))+
  geom_line(data, mapping = aes(x= Block_num, y = Total_Time, group = Participant, color = Participant), alpha = .5)+
  scale_color_viridis(option = "plasma", discrete = TRUE)+
  geom_point(data, mapping = aes(x= Block_num, y = Total_Time, group = Participant),color = 'white', size = 3)+
  geom_point(data, mapping = aes(x= Block_num, y = Total_Time, group = Participant, color = Participant),alpha = .5)+
  geom_line(data.summary, mapping = aes(x= Block_num, y = Total_Time, group = 1), size = 1.5, color = '#242526')+
  stat_summary(fun.args = list(mean_se), 
                geom="crossbar", 
                width=0.2,
                color="#242526") +
  labs(color= "Participant", y="Total Time (s)", x="")+
  scale_x_discrete(labels = c( "Block 1","Block 2","Block 3"))+
  ylim(0,1000)+
  theme_classic()+
  theme(axis.line = element_line(linewidth = .5, colour = "#242526"))+
  theme(axis.ticks = element_line(linewidth = .2, colour = "#242526"))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(size=16))+
  theme(axis.text.y = element_text(size=16))+
  theme(axis.title.y = element_text(size=16))
p_ct
```

## Stats

```{r}
# Running linear mi
m <- lmer(Total_Time ~ Block_num*Target_Name + (1|Participant), data=nav_data)
anova(m)
```
*Example for how to write up the results:*
For the effect of block: F(1,506) = 55.0636, p < 0.001

# Orientation Time

## Plot

```{r orict}
#Data.summary for Orientation_Time
data.summary <- data %>%
  group_by(Block_num) %>%
  summarise(
    se = std.error(Orientation_Time),
    Orientation_Time = mean(Orientation_Time)
  )
#Orientation Time by Block_num
p_orict <- ggplot(data, aes(x=Block_num, y=Orientation_Time, color=Participant))+
  geom_line(data, mapping = aes(x= Block_num, y = Orientation_Time, group = Participant, color = Participant), alpha = .5)+
  scale_color_viridis(option = "plasma", discrete = TRUE)+
  geom_point(data, mapping = aes(x= Block_num, y = Orientation_Time, group = Participant),color = 'white', size = 3)+
  geom_point(data, mapping = aes(x= Block_num, y = Orientation_Time, group = Participant, color = Participant),alpha = .5)+
  geom_line(data.summary, mapping = aes(x= Block_num, y = Orientation_Time, group = 1), size = 1.5, color = '#242526')+
  stat_summary(fun.args = list(mean_se), 
                geom="crossbar", 
                width=0.2, 
                color="#242526") +
  labs(color= "Participant", y="Orientation Time (s)", x="")+
  scale_x_discrete(labels = c( "Block 1","Block 2","Block 3"))+
  ylim(0,100)+
  theme_classic()+
  theme(axis.line = element_line(linewidth = .5, colour = "#242526"))+
  theme(axis.ticks = element_line(linewidth = .2, colour = "#242526"))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(size=16))+
  theme(axis.text.y = element_text(size=16))+
  theme(axis.title.y = element_text(size=16))
p_orict
```

## Stats

```{r}
# Running linear mi
m <- lmer(Orientation_Time ~ Block_num*Target_Name + (1|Participant), data=nav_data)
anova(m)
```

# Navigation Time

## Plot

```{r navct}
#Data.summary for Navigation_Time
data.summary <- data %>%
  group_by(Block_num) %>%
  summarise(
    se = std.error(Navigation_Time),
    Navigation_Time = mean(Navigation_Time)
  )
#Navigation Time by Block_num
p_navct <- ggplot(data, aes(x=Block_num, y=Navigation_Time, color=Participant))+
  geom_line(data, mapping = aes(x= Block_num, y = Navigation_Time, group = Participant, color = Participant), alpha = .5)+
  scale_color_viridis(option = "plasma", discrete = TRUE)+
  geom_point(data, mapping = aes(x= Block_num, y = Navigation_Time, group = Participant),color = 'white', size = 3)+
  geom_point(data, mapping = aes(x= Block_num, y = Navigation_Time, group = Participant, color = Participant),alpha = .5)+
  geom_line(data.summary, mapping = aes(x= Block_num, y = Navigation_Time, group = 1), size = 1.5, color = '#242526')+
  stat_summary(fun.args = list(mean_se), 
                geom="crossbar", 
                width=0.2, 
                color="#242526") +
  labs(color= "Participant", y="Navigation Time (s)", x="")+
  scale_x_discrete(labels = c( "Block 1","Block 2","Block 3"))+
  ylim(0,1000)+
  theme_classic()+
  theme(axis.line = element_line(linewidth = .5, colour = "#242526"))+
  theme(axis.ticks = element_line(linewidth = .2, colour = "#242526"))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(size=16))+
  theme(axis.text.y = element_text(size=16))+
  theme(axis.title.y = element_text(size=16))
p_navct
```

## Stats

```{r}
# Running linear mi
m <- lmer(Navigation_Time ~ Block_num*Target_Name + (1|Participant), data=nav_data)
anova(m)
```

# Distance

## Plot

```{r dt}
#Data.summary for Distance
data.summary <- data %>%
  group_by(Block_num) %>%
  summarise(
    se = std.error(Distance),
    Distance = mean(Distance)
  )
#Distance by Block_num
p_dt <- ggplot(data, aes(x=Block_num, y=Distance, color=Participant))+
  geom_line(data, mapping = aes(x= Block_num, y = Distance, group = Participant, color = Participant), alpha = .5)+
  scale_color_viridis(option = "plasma", discrete = TRUE)+
  geom_point(data, mapping = aes(x= Block_num, y = Distance, group = Participant),color = 'white', size = 3)+
  geom_point(data, mapping = aes(x= Block_num, y = Distance, group = Participant, color = Participant),alpha = .5)+
  geom_line(data.summary, mapping = aes(x= Block_num, y = Distance, group = 1), size = 1.5, color = '#242526')+
  stat_summary(fun.args = list(mean_se), 
                geom="crossbar", 
                width=0.2, 
                color="#242526") +
  labs(color= "Participant", y="Distance Traveled (VR Units)", x="")+
  scale_x_discrete(labels = c( "Block 1","Block 2","Block 3"))+
  ylim(0,5000)+
  theme_classic()+
  theme(axis.line = element_line(linewidth = .5, colour = "#242526"))+
  theme(axis.ticks = element_line(linewidth = .2, colour = "#242526"))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(size=16))+
  theme(axis.text.y = element_text(size=16))+
  theme(axis.title.y = element_text(size=16))
p_dt
```

## Stats

```{r}
# Running linear mi
m <- lmer(Distance ~ Block_num*Target_Name + (1|Participant), data=nav_data)
anova(m)
```

# Speed

## Plot

```{r speed}
#Data.summary for Speed
data.summary <- data %>%
  group_by(Block_num) %>%
  summarise(
    se = std.error(Speed),
    Speed = mean(Speed)
  )
#Speed by Block_num
p_speed <- ggplot(data, aes(x=Block_num, y=Speed, color=Participant))+
  geom_line(data, mapping = aes(x= Block_num, y = Speed, group = Participant, color = Participant), alpha = .5)+
  scale_color_viridis(option = "plasma", discrete = TRUE)+
  geom_point(data, mapping = aes(x= Block_num, y = Speed, group = Participant),color = 'white', size = 3)+
  geom_point(data, mapping = aes(x= Block_num, y = Speed, group = Participant, color = Participant),alpha = .5)+
  geom_line(data.summary, mapping = aes(x= Block_num, y = Speed, group = 1), size = 1.5, color = '#242526')+
  stat_summary(fun.args = list(mean_se), 
                geom="crossbar", 
                width=0.2, 
                color="#242526") +
  labs(color= "Participant", y="Speed (VR Unit/s)", x="")+
  scale_x_discrete(labels = c( "Block 1","Block 2","Block 3"))+
  ylim(0,23)+
  theme_classic()+
  theme(axis.line = element_line(linewidth = .5, colour = "#242526"))+
  theme(axis.ticks = element_line(linewidth = .2, colour = "#242526"))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(size=16))+
  theme(axis.text.y = element_text(size=16))+
  theme(axis.title.y = element_text(size=16))
p_speed
```

## Stats

```{r}
# Running linear mi
m <- lmer(Speed ~ Block_num*Target_Name + (1|Participant), data=nav_data)
anova(m)
```


# Dwell Time

## Plot

```{r dwell}
#Data.summary for Mean_Dwell
data.summary <- data %>%
  group_by(Block_num) %>%
  summarise(
    se = std.error(Mean_Dwell),
    Mean_Dwell = mean(Mean_Dwell)
  )
#Mean_Dwell by Block_num
p_dwell <- ggplot(data, aes(x=Block_num, y=Mean_Dwell, color=Participant))+
  geom_line(data, mapping = aes(x= Block_num, y = Mean_Dwell, group = Participant, color = Participant), alpha = .5)+
  scale_color_viridis(option = "plasma", discrete = TRUE)+
  geom_point(data, mapping = aes(x= Block_num, y = Mean_Dwell, group = Participant),color = 'white', size = 3)+
  geom_point(data, mapping = aes(x= Block_num, y = Mean_Dwell, group = Participant, color = Participant),alpha = .5)+
  geom_line(data.summary, mapping = aes(x= Block_num, y = Mean_Dwell, group = 1), size = 1.5, color = '#242526')+
  stat_summary(fun.args = list(mean_se), 
                geom="crossbar", 
                width=0.2, 
                color="#242526") +
  labs(color= "Participant", y="Mean Dwell Time (s)", x="")+
  scale_x_discrete(labels = c( "Block 1","Block 2","Block 3"))+
  ylim(0,3)+
  theme_classic()+
  theme(axis.line = element_line(linewidth = .5, colour = "#242526"))+
  theme(axis.ticks = element_line(linewidth = .2, colour = "#242526"))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(size=16))+
  theme(axis.text.y = element_text(size=16))+
  theme(axis.title.y = element_text(size=16))
p_dwell
``` 

## Stats

```{r}
# Running linear mi
m <- lmer(Mean_Dwell ~ Block_num*Target_Name + (1|Participant), data=nav_data)
anova(m)
```


# Teleportations 

## Plot

```{r teleport}
#Data.summary for Teleportations
data.summary <- data %>%
  group_by(Block_num) %>%
  summarise(
    se = std.error(Teleportations),
    Teleportations = mean(Teleportations)
  )
#Teleportations by Block_num
p_teleport <- ggplot(data, aes(x=Block_num, y=Teleportations, color=Participant))+
  geom_line(data, mapping = aes(x= Block_num, y = Teleportations, group = Participant, color = Participant), alpha = .5)+
  scale_color_viridis(option = "plasma", discrete = TRUE)+
  geom_point(data, mapping = aes(x= Block_num, y = Teleportations, group = Participant),color = 'white', size = 3)+
  geom_point(data, mapping = aes(x= Block_num, y = Teleportations, group = Participant, color = Participant),alpha = .5)+
  geom_line(data.summary, mapping = aes(x= Block_num, y = Teleportations, group = 1), size = 1.5, color = '#242526')+
  stat_summary(fun.args = list(mean_se), 
                geom="crossbar", 
                width=0.2, 
                color="#242526") +
  labs(color= "Participant", y="Teleportations (count)", x="")+
  scale_x_discrete(labels = c( "Block 1","Block 2","Block 3"))+
  ylim(0,700)+
  theme_classic()+
  theme(axis.line = element_line(linewidth = .5, colour = "#242526"))+
  theme(axis.ticks = element_line(linewidth = .2, colour = "#242526"))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(size=16))+
  theme(axis.text.y = element_text(size=16))+
  theme(axis.title.y = element_text(size=16))
p_teleport
```

## Stats
```{r}
# Running linear mi
m <- lmer(Teleportations ~ Block_num*Target_Name + (1|Participant), data=nav_data)
anova(m)
```


# Variance X

## Plot

```{r varx}
#Data.summary for Var_X
data.summary <- data %>%
  group_by(Block_num) %>%
  summarise(
    se = std.error(Var_X),
    Var_X = mean(Var_X)
  )
#Var_X by Block_num
p_varx <- ggplot(data, aes(x=Block_num, y=Var_X, color=Participant))+
  geom_line(data, mapping = aes(x= Block_num, y = Var_X, group = Participant, color = Participant), alpha = .5)+
  scale_color_viridis(option = "plasma", discrete = TRUE)+
  geom_point(data, mapping = aes(x= Block_num, y = Var_X, group = Participant),color = 'white', size = 3)+
  geom_point(data, mapping = aes(x= Block_num, y = Var_X, group = Participant, color = Participant),alpha = .5)+
  geom_line(data.summary, mapping = aes(x= Block_num, y = Var_X, group = 1), size = 1.5, color = '#242526')+
  stat_summary(fun.args = list(mean_se), 
                geom="crossbar", 
                width=0.2, 
                color="#242526") +
  labs(color= "Participant", y="X Euler Angle Variation (degrees/s)", x="")+
  scale_x_discrete(labels = c( "Block 1","Block 2","Block 3"))+
  ylim(0,20)+
  theme_classic()+
  theme(axis.line = element_line(linewidth = .5, colour = "#242526"))+
  theme(axis.ticks = element_line(linewidth = .2, colour = "#242526"))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(size=16))+
  theme(axis.text.y = element_text(size=16))+
  theme(axis.title.y = element_text(size=16))
p_varx
```

## Stats
```{r}
# Running linear mi
m <- lmer(Var_X ~ Block_num*Target_Name + (1|Participant), data=nav_data)
anova(m)
```


# Variance Y

## Plot

```{r vary}
#Data.summary for Var_Y
data.summary <- data %>%
  group_by(Block_num) %>%
  summarise(
    se = std.error(Var_Y),
    Var_Y = mean(Var_Y)
  )
#Var_Y by Block_num
p_vary <- ggplot(data, aes(x=Block_num, y=Var_Y, color=Participant))+
  geom_line(data, mapping = aes(x= Block_num, y = Var_Y, group = Participant, color = Participant), alpha = .5)+
  scale_color_viridis(option = "plasma", discrete = TRUE)+
  geom_point(data, mapping = aes(x= Block_num, y = Var_Y, group = Participant),color = 'white', size = 3)+
  geom_point(data, mapping = aes(x= Block_num, y = Var_Y, group = Participant, color = Participant),alpha = .5)+
  geom_line(data.summary, mapping = aes(x= Block_num, y = Var_Y, group = 1), size = 1.5, color = '#242526')+
  stat_summary(fun.args = list(mean_se), 
                geom="crossbar", 
                width=0.2, 
                color="#242526") +
  labs(color= "Participant", y="Y Euler Angle Variation (degrees/s)", x="")+
  scale_x_discrete(labels = c( "Block 1","Block 2","Block 3"))+
  ylim(0,130)+
  theme_classic()+
  theme(axis.line = element_line(linewidth = .5, colour = "#242526"))+
  theme(axis.ticks = element_line(linewidth = .2, colour = "#242526"))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(size=16))+
  theme(axis.text.y = element_text(size=16))+
  theme(axis.title.y = element_text(size=16))
p_vary
```

## Stats
```{r}
# Running linear mi
m <- lmer(Var_Y ~ Block_num*Target_Name + (1|Participant), data=nav_data)
anova(m)
```

 
## Plot

```{r varz}
#Data.summary for Var_Z
data.summary <- data %>%
  group_by(Block_num) %>%
  summarise(
    se = std.error(Var_Z),
    Var_Z = mean(Var_Z)
  )
#Var_Z by Block_num
p_varz <- ggplot(data, aes(x=Block_num, y=Var_Z, color=Participant))+
  geom_line(data, mapping = aes(x= Block_num, y = Var_Z, group = Participant, color = Participant), alpha = .5)+
  scale_color_viridis(option = "plasma", discrete = TRUE)+
  geom_point(data, mapping = aes(x= Block_num, y = Var_Z, group = Participant),color = 'white', size = 3)+
  geom_point(data, mapping = aes(x= Block_num, y = Var_Z, group = Participant, color = Participant),alpha = .5)+
  geom_line(data.summary, mapping = aes(x= Block_num, y = Var_Z, group = 1), size = 1.5, color = '#242526')+
  stat_summary(fun.args = list(mean_se), 
                geom="crossbar", 
                width=0.2, 
                color="#242526") +
  labs(color= "Participant", y="Z Euler Angle Variation (degrees/s)", x="")+
  scale_x_discrete(labels = c( "Block 1","Block 2","Block 3"))+
  ylim(0,10)+
  theme_classic()+
  theme(axis.line = element_line(linewidth = .5, colour = "#242526"))+
  theme(axis.ticks = element_line(linewidth = .2, colour = "#242526"))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(size=16))+
  theme(axis.text.y = element_text(size=16))+
  theme(axis.title.y = element_text(size=16))
p_varz
```

## Stats
```{r}
# Running linear mi
m <- lmer(Var_Z ~ Block_num*Target_Name + (1|Participant), data=nav_data)
anova(m)
```

